An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
abstract update in paper

---
title: "An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This paper investigates the correlation between preference and perceptions of inaction versus action in decision-making and gender to replicate on the previous studies about the findings regarding gender disparities in moral judgment preference. Building on interdisciplinary research in cognitive science, psychology, and philosophy, the study explores and examines the preference and perceived competence of different decision-making agents by gender. This report uses the  Study 2 data set from the article “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” for creating graphs and conducting statistical analysis. Since this research topic can be significant for further research, we place more weight on the discussion and further research section to inform and address the interplay of social factors."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

>>>>

---
title: "An Analysis of Preference and Percieved Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender: Men and Women Both Prefer and Percieve Inaction as More Competent"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. that broadly examined the perceptions of decision-making approaches. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical significance analysis from Fillion et al.’s  “Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes” Study 2 data. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---
